\begin{titlepage}
\begin{center}
\huge{\bf{ACKNOWLEDGEMENT\\}}\end{center}
\large{
\begin{sloppypar}
Any accomplishment requires converted efforts of many people and this project is no different. We are highly obliged and grateful to all those who have helped us in the development of this Project and provided all encouragement that has helped us immensely in our project work.
\end{sloppypar}
\begin{sloppypar}
It is our pleasure to present the project entitled \textbf{``MINING CLASSIFICATION RULES FROM DATABASE USING ARTIFICIAL NEURAL NETWORK''} which has been a throughout joint effort. Since the time we have started working on this project, we have thoroughly been engrossed with the technological exploration of the field. We acquired knowledge by reading different books and searching on the Internet.
\end{sloppypar}\begin{sloppypar}
 We take this opportunity to thank our respected \textbf{Project Guide Prof.Swati V. Shinde} without whose constant support, help and encouragement, this endeavor of ours wouldn’t have materialized.
\end{sloppypar}
\begin{sloppypar}
We thank our Principal \textbf{Dr.A.M.Fulambarkar} Project coordinator \textbf{Prof.R.G.Pise} and HOD \textbf{Prof.S.V.Shinde} for creating a wonderful learning environment. Finally, we thank all teaching and non-teaching staff who has associated directly/indirectly in the execution of this project work.
\end{sloppypar}
\begin{sloppypar}
Last but not least, we are also grateful to our friends for their valuable suggestions.\\
\end{sloppypar}}
\begin{table}[hbp]
 \begin{center}
    \begin{tabular}{   p{9cm}  l  l  }

                      \,               &    B8338503 & Prashant  P. Avaghade \\  
                       \,               &   B8338513 & Datta G. Diware \\  
                      \,                 &  B8338528 & Mahesh S. kshatriya \\  
                        \,             &    B8338559  & Nikhilesh S. Shinde \\  
                        \,             &    B8338570  & Sumit S.Wankhede \\  

    \end{tabular}
\end{center}
\end{table} 
\end{titlepage}